OptiFit project update

### 2021-03-03 docs/slides/2020-12-14_lab-mtg.Rmd
Make slides self-contained so images will show up on gh-pages

---
title: "OptiFit project update"
subtitle: "+ a case study in debugging"
author: "Kelly Sovacool"
date: "2020-12-14 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    css: [default, default-fonts]
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      #titleSlideClass: ['center', 'middle', 'title-slide']
    chakra: libs/remark-latest.min.js
---

>>>>

---
title: "OptiFit project update"
subtitle: "+ a case study in debugging"
author: "Kelly Sovacool"
date: "2020-12-14 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    css: [default, default-fonts]
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      #titleSlideClass: ['center', 'middle', 'title-slide']
    chakra: libs/remark-latest.min.js
    self_contained: true
---
